Turbulence in compact to giant H~II regions

### 2023-05-09 strucfunc_paper.tex
Javier changes 2023-05-09

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

@@

In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
which this time is due primarily to the fact that the
derived correlation length is only 6 times higher than the RMS seeing width,
so some of the small-scale fluctuation power is missing from the observations.
Of all our sources, NGC~604 shows the largest difference between the inferred
``true'' structure function and the observed one, so the derived parameters
should be treated with caution.
At the largest scales, the structure function shows a pronounced minimum
at \(r \approx \SI{150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx \SI{300}{pc}\),
which is slightly larger than the size of the map. 
\stopNEW

>>>>

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
%The uncertainty of each bin (blue error bars) is estimated
%as the standard deviation of these values divided by the square root of
%the number of contributing pairs.
\NEW{The uncertainty of each bin (blue error bars) is estimated
as the fractional error of the respective \(B\obs(r)\) value.
These values are indicated in the third column of the table given in the Appendix D. 
In the same table, the forth and fifth columns show, as multiples of their respective fractional error, additional weight at small and large scales. 
This is the case for the EON, and the regions observed using the FLAMES and the TAURUS instruments.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

@@

In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
which this time is due primarily to the fact that the
derived correlation length is only 6 times higher than the RMS seeing width,
so some of the small-scale fluctuation power is missing from the observations.
Of all our sources, NGC~604 shows the largest difference between the inferred
``true'' structure function and the observed one, so the derived parameters
should be treated with caution.
At the largest scales, the structure function shows a pronounced minimum
at \(r \approx \SI{150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx \SI{300}{pc}\),
which is slightly larger than the size of the map. 
On the other hand, if we fit the model for scales \(r \leq \SI{20}{pc}\), there is a decrease in the difference between the inferred ``true'' structure function and the observed one. With our current observations the fitting using less than half of the observational points cannot be justified; but with better quality observations and using our current model we would expect to derived more accurate parameters.
\stopNEW
